Calendar-based graphics for visualizing people's daily schedules

### 2018-10-08 main.Rmd
added weekend mapping

```{r ped-map, fig.width = 4, out.width = "0.55\\linewidth", fig.cap = "Map of the Melbourne city area with purple dots indicating sensor locations."}
```

@@

```{r flinders-2016, fig.height = 6.5, fig.cap = "The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a $3 \times 4$ monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent."}
```

@@

```
frame_calendar(
  data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
  scale = "fixed", width = 0.95, height = 0.95
)
```

@@

```{r facet, fig.height = 11, fig.cap = "Line charts, embedded in the $6 \times 2$ monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors."}
```

>>>>

```{r ped-map, fig.width = 7, out.width = "0.7\\linewidth", fig.cap = "Map of the Melbourne city area with dots indicating sensor locations. 3 sensors have been highlighted to give a closer look at in the paper."}
```

@@

```{r flinders-2016, fig.height = 6.5, fig.cap = "The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a 3 by 4 monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent."}
```

@@

```
frame_calendar(
  data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
  scale = "fixed", width = 0.95, height = 0.95, margin = NULL
)
```

@@

```{r facet, fig.height = 11, fig.cap = "Line charts, embedded in the 6 by 2 monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors."}
```

### 2018-10-08 main.tex
added weekend mapping

{\centering \includegraphics[width=0.55\linewidth]{figure/ped-map-1}

@@

\caption[Map of the Melbourne city area with purple dots indicating sensor locations]{Map of the Melbourne city area with purple dots indicating sensor locations.}\label{fig:ped-map}
\end{figure}
\end{Schunk}

@@

\caption[The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs]{The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a $3  imes 4$ monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent.}\label{fig:flinders-2016}
\end{figure}
\end{Schunk}

@@

\begin{verbatim}
frame_calendar(
  data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
  scale = "fixed", width = 0.95, height = 0.95
)
\end{verbatim}

@@

\caption[Line charts, embedded in the $6    imes 2$ monthly calendar, colored and faceted by the 3 sensors]{Line charts, embedded in the $6     imes 2$ monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.}\label{fig:facet}
\end{figure}
\end{Schunk}

>>>>

{\centering \includegraphics[width=0.7\linewidth]{figure/ped-map-1}

@@

\caption[Map of the Melbourne city area with dots indicating sensor locations]{Map of the Melbourne city area with dots indicating sensor locations. 3 sensors have been highlighted to give a closer look at in the paper.}\label{fig:ped-map}
\end{figure}
\end{Schunk}

@@

\caption[The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs]{The calendar-based display of hourly foot traffic at Flinders Street Station using line glyphs. The arrangement of the data into a 3 by 4 monthly grid represents all the traffic in 2016. The disparities between week day and weekend along with public holiday are immediately apparent.}\label{fig:flinders-2016}
\end{figure}
\end{Schunk}

@@

\begin{verbatim}
frame_calendar(
  data, x, y, date, calendar = "monthly", dir = "h", 
  sunday = FALSE, nrow = NULL, ncol = NULL, polar = FALSE, 
  scale = "fixed", width = 0.95, height = 0.95, margin = NULL
)
\end{verbatim}

@@

\caption[Line charts, embedded in the 6 by 2 monthly calendar, colored and faceted by the 3 sensors]{Line charts, embedded in the 6 by 2 monthly calendar, colored and faceted by the 3 sensors. The variations of an individual sensor are emphasised, and the shapes can be compared across the cells and sensors.}\label{fig:facet}
\end{figure}
\end{Schunk}
